Self-test prime dimensional EPR pairs with constant alphabet

### 2019-02-06 Draft/draft.tex
Honghao: finished rewriting sec. 5.1

@@

\def\carl#1{{\color{blue} #1 -Carl}}

@@

\textbf{The ideal strategy for $\LS_r$}.
We denote the number of generators labelled by $x_i$ in $\LS_r$ by $n_r(x)$.
In order to construct a representation of $\Gamma(\LS_r)$, we first construct a representation, $\Psi_{G(x)}$ for the group 
\begin{align}
	G(x) = \ip{ \{x_i\}_{i=1}^{n_r(x)}: x_i^2 = e, x_i x_j x_i = x_k \text{ for all } (i,j,k) \in C_r},
\end{align}
where details of $C_r$ can be found in the appendices. 
Note that the relation $uxu^{-1} = x^2$ is embedded in the conjugation relations in $C_r$.
Building on $\Psi_{G(x)}$, we can construct
the representation $\Psi_{\Gamma(\LS_r)}$ for the solution group $\Gamma(\LS_r)$.

@@

the observables $A_1 = B_1 = \Psi_{G(x)}(x_1)$ and $A_2 = B_2 = \Psi_{G(x)}(x_2)$ are extended from $B_1|_V$ and $B_2|_V$ as follows

@@

	A_1 = B_1 = \Psi_{G(x)}(x_1) &= \sum_{k=1}^{(d-1)/2}\left( \omega_d^k\ketbra{x_k}{x_{d-k}} + \omega_d^{-k}\ketbra{x_{d-k}}{x_k}\right)\\
	A_2 = B_2 = \Psi_{G(x)}(x_2) &= \sum_{k=1}^{(d-1)/2}\left(\ketbra{x_{d-k}}{x_k} + \ketbra{x_k}{x_{d-k}}\right).

@@

It can be checked that $X = \Psi_{G(x)}(x_1x_2) = \sum_{i=1}^{d-1} \omega_d^i \ketbra{x_i}{x_i}$ 

@@

	U =\Psi_{G(x)}(u) = \Psi_{G(x)}(x_3x_4) =  \sum_{i=1}^{d-1} \ketbra{x_{i/r \pmod{d}}}{x_i}.

@@

then give $\Psi_{G(x)}(x_3)$ and $\Psi_{G(x)}(x_4)$.

@@

The decomposition of $U$ into $\Psi_{G(x)}(x_3)$ and $\Psi_{G(x)}(x_4)$ is similar to the decomposition of $X$.

@@

then $\Psi_{G(x)}(x_3)$ and $\Psi_{G(x)}(x_4)$ are  

@@

	A_3 = B_3 =\Psi_{G(x)}(x_3) = &\ketbra{u_0}{u_0} +\omega_{d-1}^{(d-1)/2}\ketbra{u_{(d-1)/2}}{u_{(d-1)/2}}\\ + 

@@

	A_4 = B_4  =\Psi_{G(x)}(x_4) = &\ketbra{u_0}{u_0} +\ketbra{u_{(d-1)/2}}{u_{(d-1)/2}} \\+

@@

	\Psi_{G(x)}(x_5) = \Psi_{G(x)}(x_1)\Psi_{G(x)}(x_2) \Psi_{G(x)}(x_1).

@@

Next, we consider the representation $\Psi_{G(x,y,z,w)}$.
In the next step of embedding, for each $x_i$, we find $y_i$ ,$z_i$, $w_i$ and $f$ such that
$x_i = y_iz_i = fw_i$. We demonstrate how this splitting is done by pick $x_1$ as an example, 
which is mapped to $B_1$ in the previous step. Now we map $x_1$ to $B_1'$ which is
\begin{align}
	B_1' = \begin{pmatrix}
	B_1 & 0 \\
	0 & B_1
	\end{pmatrix},
\end{align}
then $y_1$, $z_1$, $w_1$ and $f$ are mapped to
\begin{align}
y_1 \to 
\begin{pmatrix}
B_1 & 0\\
0 & \1
\end{pmatrix},
&&
z_1 \to
\begin{pmatrix}
\1 & 0\\
0 & B_1
\end{pmatrix},
\\
w_1 \to 
\begin{pmatrix}
0 & B_1\\
B_1 & 0
\end{pmatrix},
&&
f \to
\begin{pmatrix}
0 & \1\\
\1 & 0
\end{pmatrix}.
\end{align}

The last step of embedding follows the same manner as we double the dimension of the operators again.
For example, $y_1$ is mapped to $B_1 \oplus \1 \oplus B_1 \oplus \1$ and $z_1$ is mapped to 
$\1 \oplus B_1 \oplus \1 \oplus B_1$, so effectively, $x_1$ is mapped to $B_1^{\oplus 4}$.
\footnote{Details of this step of embedding can be found in proof of Proposition~$4.2$ in Ref.~\cite{slofstra2017}.}

In the end, we determine the shared state.
The optimal correlation for $\CHSH_X$ uses state 
$\ket{\psi} = \frac{1}{\sqrt{d-1}} \sum_{i=1}^{d-1} \ket{u_i}\ket{u_i}$, 
so the shared state for $\G$ is $\frac{1}{2}( \ket{\psi}^{\oplus 4})$.
\end{proof}
Next we are going to prove that the correlation $C(\dr{r})$, which is produced by the 
strategy winning this game optimally, can self-test $d-1$-dimensional EPR pair.

>>>>

% Comments
\def\carl#1{{\color{blue} #1 -Carl}}
\newcommand{\hf}[1]{\textcolor{red}{#1}}

@@

@@

\textbf{The ideal strategy for $\LS_r$}.
We denote the number of generators labelled by $x_i$ in $\LS_r$ by $n_r(x)$.
In order to construct a representation of $\Gamma(\LS_r)$, we first construct a representation, $\Psi_1$ for the group 
\begin{align}
	G_r(x) = \ip{ \{x_i\}_{i=1}^{n_r(x)}: x_i^2 = e, x_i x_j x_i = x_k \text{ for all } (i,j,k) \in C_r},
\end{align}
where details of $C_r$ can be found in the appendices. 
Note that the relation $uxu^{-1} = x^r$ is embedded in the conjugation relations in $C_r$.
Building on $\Psi_1$, we can construct 
the representation $\Psi_{\LS_r}$ for the solution group $\Gamma(\LS_r)$.

@@

the observables $A_1 = B_1 = \Psi_1(x_1)$ and $A_2 = B_2 = \Psi_1(x_2)$ are extended from $B_1|_V$ and $B_2|_V$ as follows

@@

	A_1 = B_1 = \Psi_1(x_1) &= \sum_{k=1}^{(d-1)/2}\left( \omega_d^k\ketbra{x_k}{x_{d-k}} + \omega_d^{-k}\ketbra{x_{d-k}}{x_k}\right)\\
	A_2 = B_2 = \Psi_1(x_2) &= \sum_{k=1}^{(d-1)/2}\left(\ketbra{x_{d-k}}{x_k} + \ketbra{x_k}{x_{d-k}}\right).

@@

It can be checked that $X = \Psi_1(x_1x_2) = \sum_{i=1}^{d-1} \omega_d^i \ketbra{x_i}{x_i}$ 

@@

	U =\Psi_1(u) = \Psi_1(x_3x_4) =  \sum_{i=1}^{d-1} \ketbra{x_{i/r \pmod{d}}}{x_i}.

@@

then give $\Psi_1(x_3)$ and $\Psi_1(x_4)$.

@@

The decomposition of $U$ into $\Psi_1(x_3)$ and $\Psi_1(x_4)$ is similar to the decomposition of $X$.

@@

then $\Psi_1(x_3)$ and $\Psi_1(x_4)$ are  

@@

	A_3 = B_3 =\Psi_1(x_3) = &\ketbra{u_0}{u_0} +\omega_{d-1}^{(d-1)/2}\ketbra{u_{(d-1)/2}}{u_{(d-1)/2}}\\ + 

@@

	A_4 = B_4  =\Psi_1(x_4) = &\ketbra{u_0}{u_0} +\ketbra{u_{(d-1)/2}}{u_{(d-1)/2}} \\+

@@

	\Psi_1(x_5) = \Psi_1(x_1)\Psi_1(x_2) \Psi_1(x_1).

@@

Next, we consider the representation $\Psi_2$ for the group 
\begin{align*}
	G(x,y,z,w) = \ip{ \{x_i, w_i, y_i, z_i\}_{i=1}^{n_r(x)}, f, \{g_{jk}\}_{(i,j,k) \in C_r} :&\text{all elements are of order $2$},\\
	&x_i = y_iz_i = fw_i,\; fy_if =z_i \text{ for } i= 1 \dots n_r(x) \\
	&g_{jk}y_j z_k = e,\; w_iy_jw_i = z_k \text{ for all } (i,j,k)\in C_r}.
\end{align*}
The representation $\Psi_2$ of $G(x,y,z,w)$ should satisfy the condition that for each $x_i$, 
$\Psi_2(x_i) = \Psi_2(y_i)\Psi_2(z_i) = \Psi_2(f)\Psi_2(w_i)$. We demonstrate how this representation is constructed 
for $x_i$, $y_i$, $z_i$, $w_i$ and $f$ where $i = 1 \dots n_r(x)$.
Building on $\Psi_1$, we have $\Psi_2(x_i) = \Psi_1(x_i) \oplus \Psi_1(x_i)$, then
$y_i$, $z_i$, $w_i$ and $f$ are mapped to
\begin{align*}
\Psi_2(y_i) = 
\begin{pmatrix}
\Psi_1(x_i) & 0\\
0 & \1
\end{pmatrix},
&&
\Psi_2(z_i) \to
\begin{pmatrix}
\1 & 0\\
0 & \Psi_1(x_i)
\end{pmatrix},
\\
\Psi_2(w_i) = 
\begin{pmatrix}
0 & \Psi_1(x_i)\\
\Psi_1(x_i) & 0
\end{pmatrix},
&&
\Psi_2(f) \to
\begin{pmatrix}
0 & \1\\
\1 & 0
\end{pmatrix}.
\end{align*}
It can be easily checked that the order-$2$ generators are mapped to order-$2$ operators and
the relations satisfied by the generators are preserved.
For each $g_{jk}$ where $(i,j,k) \in C_r$, $\Psi_2(g_{jk}) = \Psi_2(y_j)\Psi_2(z_k)$ following
their defining relations.

The group $G_r(x,y,z,w)$ is embedded in $\Gamma(\LS_r)$ by replacing the conjugacy relations 
by linear relations. The new generators are $\{\{y_{F_j,k}\}_{k=1}^6\}_{j=1}^{n_r(x)}
\cup \{\{y_{K,k}\}_{k=1}^7\}_{K \in C_r}$. How the new linear relations can embed the conjugacy relations 
in $G_r(x,y,z,w)$ can be found in the appendices. Now we define the representation $\Psi_{\LS_r}$ of
$\Gamma(\LS_r)$. For any generator $a \in \{x_i, w_i, y_i, z_i\}_{i=1}^{n_r(x)}, f, \{g_{jk}\}_{(i,j,k) \in C_r}$,
\begin{align}
	\Psi_{\LS_r}(a) = \Psi_2(a) \oplus \Psi_2(a) = \Psi_1(a)^{\oplus 4}.
\end{align}
For generators $\{y_{F_j,k}\}_{k=1}^7\}_{j=1}^{n_r(x)}$,
\begin{align*}
	\Psi_{\LS_r}(y_{F_j,1}) = 
	\begin{pmatrix}
		0 & \Psi_2(f) \\
		\Psi_2(f) & 0
	\end{pmatrix},
	&&
	\Psi_{\LS_r}(y_{F_j,2}) = 
	\begin{pmatrix}
		0 & \1\\
		\1 & 0
	\end{pmatrix},\\
	\Psi_{\LS_r}(y_{F_j,3}) = 
	\begin{pmatrix}
		0 & \Psi_2(y_j) \\
		\Psi_2(y_j) & 0
	\end{pmatrix},
	&&
	\Psi_{\LS_r}(y_{F_j,4}) = 
	\begin{pmatrix}
		0 & \Psi_2(y_jf) \\
		\Psi_2(fy_j) & 0
	\end{pmatrix},\\
	\Psi_{\LS_r}(y_{F_j,5}) = 
	\begin{pmatrix}
		 \Psi_2(fy_jf) & 0\\
		  0 & \Psi_2(f)
	\end{pmatrix},
	&&
	\Psi_{\LS_r}(y_{F_j,6}) = 
	\begin{pmatrix}
		 \Psi_2(y_jz_j) & 0\\
		 0 & \1
	\end{pmatrix},\\
	\Psi_{\LS_r}(y_{F_j,7}) = 
	\begin{pmatrix}
		 \Psi_2(y_j) & 0\\
		 0 & \Psi_2(z_j)
	\end{pmatrix}.
\end{align*}
For generators $\{\{y_{K,k}\}_{k=1}^7\}_{K=(k_1,k_2,k_3) \in C_r}$,
\begin{align*}
	\Psi_{\LS_r}(y_{K,1}) = 
	\begin{pmatrix}
		0 & \Psi_2(w_{k_1}) \\
		\Psi_2(w_{k_1}) & 0
	\end{pmatrix},
	&&
	\Psi_{\LS_r}(y_{F_j,2}) = 
	\begin{pmatrix}
		0 & \1\\
		\1 & 0
	\end{pmatrix},\\
	\Psi_{\LS_r}(y_{F_j,3}) = 
	\begin{pmatrix}
		0 & \Psi_2(y_{k_2}) \\
		\Psi_2(y_{k_2}) & 0
	\end{pmatrix},
	&&
	\Psi_{\LS_r}(y_{F_j,4}) = 
	\begin{pmatrix}
		0 & \Psi_2(y_{k_2}w_{k_1}) \\
		\Psi_2(w_{k_1}y_{k_2}) & 0
	\end{pmatrix},\\
	\Psi_{\LS_r}(y_{F_j,5}) = 
	\begin{pmatrix}
		 \Psi_2(w_{k_1}y_{k_2}w_{k_1}) & 0\\
		  0 & \Psi_2(w_{k_1})
	\end{pmatrix},
	&&
	\Psi_{\LS_r}(y_{F_j,6}) = 
	\begin{pmatrix}
		 \Psi_2(y_{k_2}z_{k_3}) & 0\\
		 0 & \1
	\end{pmatrix},\\
	\Psi_{\LS_r}(y_{F_j,7}) = 
	\begin{pmatrix}
		 \Psi_2(y_{k_2}) & 0\\
		 0 & \Psi_2(z_{k_3})
	\end{pmatrix}.
\end{align*}

In the end, to compensate the enlarged Hilbert space, the shared state is $\frac{1}{2}( \ket{\psi}^{\oplus 4})$,
where $\ket{\psi} = \frac{1}{\sqrt{d-1}} \sum_{i=1}^{d-1} \ket{i}\ket{i}$.
At the same time, the observables for the extended weighted CHSH test are mapped to four copies of themselves. 
\end{proof}
Next we are going to prove that the correlation $C(\dr{r})$, which is produced by the 
strategy winning this game optimally, can self-test $d-1$-dimensional EPR pair.
